\documentclass[11pt,a4paper]{scrartcl}
\usepackage[ngerman]{babel}

\usepackage[T1]{fontenc}      % T1-encoded fonts: auch W?rter mit Umlauten trennen
\usepackage[latin1]{inputenc}

\usepackage{currvita}


\usepackage{relsize}
\usepackage{soul}
\usepackage{xspace}


\usepackage[final]{graphicx}  % um Graphiken einzubinden
%\usepackage{picins} %fuer bild einfuegen
\usepackage{picinpar}


\newcommand{\versal}[1]{\textsf{\textsmaller{\MakeUppercase{\caps{#1}}}}\xspace}

\newcommand*{\ac}[1]{\versal{#1}}
\tolerance=600
%%% % make sure everything fits on one page
\textheight=680pt %%% % increase textheight from default 595pt
\pagestyle{empty} %%% % remove pagenumber
\date{}

\begin{document}


\begin{center}
  \Large{List of Publications}
\end{center}

\textbf{Papers} \\
\begin{enumerate}
\item Cannarozzi G, Schraudolph NN, Faty M, von Rohr P, Friberg MT, Roth AC, Gonnet P, 
  Gonnet G, and Barral Y (2010)
  A Role for Codon Order in Translation Dynamics.
  Cell Volume 141, Issue 2:355-367 
\item Kangas-Kontio T, Kakko S, Tamminen M, von Rohr P, Hoeschele I, Juvonen T, Kere J 
  and Savolainen MJ (2009)
  Genome scan for loci regulating HDL cholesterol levels in Finnish extended pedigrees 
  with early coronary heart disease.
  European Journal of Human Genetics (2010) 18:604-613
\item von Rohr P, Friberg MT and Kadarmideen HN (2007)
  Prediction of Transcription Factor Binding Sites Using Genetical Genomics Methods. 
  Journal of Bioinformatics and Computational Biology Vol. 5, No. 3:773-793
\item Kadarmideen HN, von Rohr, P, Janss LLG (2006) 
  From genetical genomics to systems genetics: potential applications in 
  quantitative genomics and animal breeding. Mammalian Genome 17:548-564.
\item Markus Friberg, Peter von Rohr and Gaston Gonnet 2005. 
  Scoring functions for transcription factor binding site predictions. 
  BMC Bioinformatics 2005, 6:84.
\item Wille A, Zimmermann P, Vranov\/a E, Bleuler S,   F\"urholz A, Hennig L, 
  Laule O, Prel\/ic A, von Rohr P, Thiele L, Zitzler E, Gruissem W, B\"uhlmann P (2004) 
  Sparse graphical Gaussian modeling of the isoprenoid gene network in 
  \textit{Arabidopsis thaliana}. Genome Biology 2004, 5:R92.
\item Markus Friberg, Peter von Rohr and Gaston Gonnet 2004. 
  Codon usage and protein expression in Saccharomyces cerevisiae. 
  Yeast 2004,21, 108-109.
\item Markus Friberg, Gaston Gonnet, Peter von Rohr and Kurt Tobler 2003. 
  Phylogenetic trees based on k-nucleotide frequencies. 
  (Techreport CBRG 2013)
\item Sakari Kakko, Jani Kelloniemi, Peter von Rohr, Ina Hoeschele, Minna 
  Tamminen, Margaret E. Brousseau, Y. Antero Kes\"aniemi, and Markku J. 
  Savolainen 2002. 
  ATP-binding cassette transporter A1 locus is not a major determinant of 
  HDL-C levels in a population at high risk for coronary heart disease. 
  Arterisclerosis, Thrombosis, and Vascular Biology (accepted) 
\item Peter von Rohr  and Ina Hoeschele 2002. Robust Bayesian QTL mapping using skewed Student-t distributions. Genet. Sel. Evol. 34 (2002) 1-21. 
\item Peter von Rohr, Andreas Hofer and Niklaus Kuenzi 1999. Economic values of meat quality traits in pigs. Journal of Animal Science 77 (10): 2633 - 2640.
\item Peter von Rohr, Andreas Hofer and Niklaus Kuenzi 1999. Two growth models to estimate economic values for feed intake capacity in pigs. Animal Science 69: 49 - 57.
\item Peter von Rohr, Andreas Hofer and Niklaus Kuenzi 1994. Wirtschaftliche Gewichte in der Schweineproduktion. Agrarforschung 11/12: 488 - 491.


%\pagebreak
\vspace{2ex}
\noindent\textbf{Invited Reviews}
\item Peter von Rohr 2003. Book Review on Introduction to Computational Biochemistry 
  by C. Stan Tsai. ChemBioChem Volume 4, Issue 4, p 349.

\vspace{2ex}
\noindent\textbf{Abstracts and other Publications}
\item C.F. Baes, P. von Rohr, M.A. Dolezal, E. Fritz-Waters, B. Bapst, C. Flury, 
  H. Signer-Hasler, C. Stricker, R. Fernando, F. Schmitz-Hsu, D.J. Garrick, 
  J.M. Reecy and B. Gredler 2014.
  The effect of read coverage in whole genome sequencing data.
  $65?{th}$ Annual Meeting of the European Federation of Animal Science, 
  Kopenhagen Denmark.
\item Ulrike Janssen-Tapken, Haja N. Kadarmideen and Peter von Rohr 2006. 
  Cattle Breeding Strategies using Genetic Markers as a Pathway
  for Improving Competitiveness of Pastoral Systems in Kenya.
  Conference on Pastoralism and Poverty Reduction
  in East Africa: A policy Research Conference to be held in June 27-28,
  Nairobi, Kenya
\item Markus Friberg, Gaston Gonnet, Peter von Rohr and Kurt Tobler 2004.
  Phylogenetic trees based on k-nucleotide frequencies.
  Techreport 401, Departement Informatik, ETH Zurich. (submitted to J Comp Biol)
\item Amela Prelic, Stefan Bleuler, Philip Zimmermann, Peter von Rohr, Anja Wille, 
  Peter B\"uhlmann, Wilhelm Gruissem, Lothar Thiele and Eckhart Zitzler 2004. 
  Studying the Usefulness of Biclustering on a Global Scale. (submitted to ISMB/ECCB).
\item Anja Wille, Philip Zimmermann, Stefan Bleuler, Lars Henning, Amela Prelic, 
  Peter von Rohr, Lothar Thiele, Eckhart Zitzler, Wilhelm Gruissem and Peter B\"uhlmann 2004. 
  Adjusting graphical models for reverse engineering of genetic regulatory networks. 
  (submitted to ISMB/ECCB).
\item von Rohr P. Developing Statistical Methods in Genetics and Bioinformatics. Invited 
  Seminar at Hoffmann-La Roche Basel, July 10, 2003. Talk.
\item von Rohr P., Cannarozzi G., Roth A., Friberg M., Gonnet P., Faty M., Barral Y., and Gonnet G. Autocorrelation in Coding DNA Sequences of Four Organisms. Joining Forces: Intersections between Biology, Chemistry, Engineering and Informatics, Mini-Symposium, ETH Zuerich Hoenggerberg, March 18, 2003. Poster 19.
\item von Rohr P. Bayesian Networks and their Applications in Genetics. Graphical Models and Bayesian Networks, Seminar ETHZ, January 14 2003. 
\item von Rohr P. Autocorrelation Analysis of DNA Sequences in Yeast. CoLab Symposium ETHZ, January 7 2003. 
\item von Rohr P. Simulating Gene-Interaction Networks. ETHZ Computation and Biology Day, CoLab ETHZ, November 22 2002.
\item von Rohr P. Learning Structure from Data In: "Probabilistic Reasoning in Intelligent Systems", J. Pearl. Graphical Models and Bayesian Networks, Seminar ETHZ, November 19 2002. 
\item von Rohr P. Bayesian versus Frequentist Approaches. Graphical Models and Bayesian Networks, Seminar ETHZ, November 5 2002.
\item von Rohr P., Roth A., and Frey J. 2002. Oligonucleotide Selection for Molecular Taxa Classification via Microarray Technology Using Multiple Sequence Alignments. European Conference on Computational Biology, October 6-9, Saarbr\"ucken. Poster 172.
\item von Rohr P. 2002. Activity Report of Working Group 3 in COST 853.
\item von Rohr P. and Frey J. 2002. The Intelligent Chip - A Design Proposal. Combined Meeting of Working Groups 1 and 3 of COST 853. September 26-28, W\"adenswil, Switzerland. Poster.
\item von Rohr P. 2002. Agricultural Biomarkers for Array Technology. Readings in BioInformatics Institute for Theoretical Computer Science, ETHZ. April 24, 2002.
\item von Rohr P. 2002. Microarrays. Readings in BioInformatics Institute for Theoretical Computer Science, ETHZ. January 13, 2002.
\item Hoeschele I., Du F.X., Thaller G., and von Rohr P. 2001. QTL Mapping in Complex Pedigrees. Plant \& Animal Genome Conference IX, San Diego, USA. January 13-17. Talk at Workshop on Statistical Genetics 
\item von Rohr P. and Hoeschele I. 2001. GENOTYPE  SAMPLING IN COMPLEX PEDIGREES VIA ALLELIC PEELING ALGORITHMS. Plant \& Animal Genome Conference IX, San Diego, USA. January 13-17. Poster.
\item von Rohr P. 2000. Statistical analysis of data from cDNA microarrays. 78th Meeting of the Statistical Genetics Committee of DgfZ, Grub, Germany, March 27-29. Talk.
\item von Rohr P. and Hoeschele I. 2000. Robust Bayesian polygene mapping using skewed Student-t distributions. Plant \& Animal Genome Conference VIII, San Diego, USA. January 9-12. Poster.
\item von Rohr P., Sun Y-H., Alscher R., Sederoff R., Whetten R. and Hoeschele I. 1999. Quantitative analysis of gene expression patterns seen on microarrays of Pinus taeda xylem cDNA. Workshop on Microarray Algorithms and Statistical Analysis Methods and Standards. Granlibakken at Lake Tahoe, USA, November 9 - 12. Poster. 
\item von Rohr P. and Hoeschele I. 1999. Robust Bayesian analysis using skewed Student-t distributions. 50th Annual Meeting of the European Association of Animal Production.  Zurich, Switzerland, August 22 - 26, Paper G3.7. 
\item Hofer A. and von Rohr P. 1998. Economic values for meat quality and food intake capacity in pigs. International Workshop on Introduction of BLUP Animal Model in Pigs. Research Institute of Animal Production, Praha - Uhrineves, Czech Republic, September 3-5. Talk. 
\item von Rohr P., Hofer A. and Kuenzi N. 1998. Wirtschaftliche Bedeutung von Fleischqualitaetsmerkmalen. LBL - Kurs: Schweinehaltung 98, LBBZ Ruetti Zollikofen, Mai 26-28. Talk.
\item von Rohr P., Hofer A. and Kuenzi N. 1997. Expected selection response for alternative breeding goals in pigs. 48th Annual Meeting of the European Association for Animal Production, Vienna, Austria, August 25-28. Talk.
\item von Rohr P., Hofer A. and Kuenzi N. 1997. Bio-oekonomische Modelle zur Ableitung des wirtschaftlichen Gewichtes fuer die Futteraufnahme beim Schwein. Vortragstagung der DgfZ/GfT, Bonn, Deutschland, September 10-11. Talk. 
\item von Rohr P., Hofer A. and Kuenzi N. 1996. Assessment of meat quality criteria  by the slaughter and retail industry. Proc. 42nd International Conference for Meat Science and Technology, Lillehammer, Norway, September 1-6. Poster. 
\item von Rohr P., Hofer A. and Kuenzi N. 1996. Economic values for meat quality traits in pigs. 47th Annual Meeting of the European Association for Animal Production, Lillehammer, Norway, August 26-29. Talk. 
\item von Rohr P., Hofer A. and Kuenzi N. 1996. Wirtschaftliche Bedeutung von Schlachtkoerperqualitaetsmerkmalen beim Schwein. Sommertagung der Schweizerischen Vereinigung fuer Tierzucht, Zuerich, Schweiz, August 22. Talk.
\item von Rohr P., Hofer A. and Kuenzi N. 1994. Wirtschaftliche Gewichte in der Schweineproduktion - Ein Vergleich zwischen Deutschland und der Schweiz. Vortragstagung der DgfZ/GfT, Halle, Deutschland, September 14-15. Talk. 
\item von Rohr P., Hofer A. and Kuenzi N. 1994. Vergleich der wirtschaftlichen Produktionsbedinungen zwischen der Schweiz und der EU. LBL - Kurs: Schweinehaltung 94, Ins, Schweiz, Mai 18-19. Talk.

\vspace{2ex}
\noindent\textbf{Theses}
\item von Rohr P. 1998. Wirtschaftliche Gewichte fuer Mastleistungs- und Schlachtkoerperqualitaetsmerkmalen beim Schwein. Dissertation ETH Zurich Nr. 12733.
\item von Rohr P. 1993. Energie- und Proteinbedarf des Kalbes. Diplomarbeit RAP Posieux and ETH Zurich.
\end{enumerate}

\end{document}
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "CVResearchMain"
%%% End: 
